Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-02 thesis/acm/paper.tex
notes

\textbf{Background } 
Studies of the motives and drivers behind modifications to APIs have been done before, but platform APIs are, so far, unexplored. Previous work has also not studied APIs from the perspective of widely recognised software evolution theories, such as the Categories of Software Maintenance and Lehman's laws of software evolution.

@@

Each change between versions has been identified and grouped into four particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends. Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories. Each change was given a main category of maintenance and a subcategory if appropriate. This information will be used to answer \textbf{RQ1} and \textbf{RQ1.1}.

%%Does this paragraph below belong here or somewhere else? Feels a bit odd!
The API itself consisted of two major versions; 1.4 and 2.0. There were no intermediate versions between 1.4 and 2.0. Version 1.4 was actually the same version as 1.0, just with added build options for other hardware platforms. The changes therefore come from the changes between the two major versions. Given that there was an apparent "big bang" implementation of the new API, we have tried to determine what existed in the previous version, what was re-implemented and what is brand new.

@@

For future studies, this technique could be improved by performing more actions along side the code review. For example, having access to and analysing commit logs, design meetings and other such documentation would allow a much more thorough determination of intents to be collected and analysed.

This should probably be in conclusion, right? /Willy
       What this means for industry:
       	Greater emphasis should be placed upon communicating with the end users / application developers. APIs should be made with maintainability and extendibility in mind as they seem to be what changes the most between versions. They should probably improve their feedback system to get more feedback from the API users.

>>>>

\textbf{Background } 
Studies of the motives and drivers behind modifications to APIs have been done before, but platform APIs are, so far, unexplored. Previous work has also not studied APIs from the perspective of widely recognised software evolution theories, such as the Types of Software Evolution and Software Maintenance and Lehman's laws of software evolution.

@@

%This should probably go in Methodology... parts of it at least /W
Each change between versions has been identified and grouped into four particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends. Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories. Each change was given a main category of maintenance and a subcategory if appropriate. This information will be used to answer \textbf{RQ1} and \textbf{RQ1.1}.

%%Does this paragraph below belong here or somewhere else? Feels a bit odd!    W: Case Company Description I think
The API itself consisted of two major versions; 1.4 and 2.0. There were no intermediate versions between 1.4 and 2.0. Version 1.4 was actually the same version as 1.0, just with added build options for other hardware platforms. The changes therefore come from the changes between the two major versions. Given that there was an apparent "big bang" implementation of the new API, we have tried to determine what existed in the previous version, what was re-implemented and what is brand new.

@@

For future studies, this technique could be improved by performing more actions along side the code review. For example, having access to and analysing commit logs, design meetings and other such documentation would allow a much more thorough determination of intents to be collected and analysed. %%Conclusion stuff /Willy

%%The following should probably be in conclusion, right? /Willy
       What this means for industry:
       	Greater emphasis should be placed upon communicating with the end users / application developers. APIs should be made with maintainability and extendibility in mind as they seem to be what changes the most between versions. They should probably improve their feedback system to get more feedback from the API users.
